### 2016-11-15 thesis/intro/intro.tex
finished impact of obesity subsection

posing threat to the growing population that are becoming more obese.

\citep{Malik2013, Franks2010}

>>>>

Overweight and obesity have been a risk factor for many diseases, including type 2 diabetes, cardiovascular diseases, hypertension, and many types of cancers \citep{Franks2010, Guh2009, Yach2006}.
As \citet{Yach2006} mentions in their paper, ``overweight and obesity have become to diabetes what tobacco is to lung cancer'', and it is important to understand that obesity has significant risks and comorbidities associated with it.

Although adulthood obesity is clinically important for risk assessment of diseases, childhood obesity has been focussed more heavily in recent years,  as it has greater public health implications.
There are many immediate consequences that are related to childhood obesity, but the diseases that develop as these children grow up are more critical than the earlier effects.

In the paper written by \citet{Must1999}, they reviewed many of the clinical studies done in the 1900s and summarised the risks associated with childhood obesity.
Among the many risks associated with obesity, obese children, compared to lean children, had over 8.5-fold increased risk of developing hypertension as adults \citep{Must1999}.
On top of this, the relative risks for all-cause mortality and coronary heart disease-specific mortality were 1.5 and 2.5, respectively \citep{Must1999}.

In a more recent paper by \citep{Franks2010}, they have shown that childhood obesity (as well as glucose intolerance and hypertension in childhood) was strongly associated with premature deaths from endogenous causes in American Indian population from Arizona (incidence rate ratio of 1.4 per unit of \gls{bmi} z-score).\\

\noindent
Health related consequences of obesity are clear from these studies, but it is noteworthy that obesity also has an economical impact on the population as well.
In the \gls{usa}, within the span of 5 years, the medical cost due to diabetes have risen from \$44 billion to \$92 billion \citep{Yach2006}.
Although not all diabetes are directly caused by obesity, obesity would have assisted in the rise in the costs associated with diabetes.
In addition to this, the costs that are associated with diabetes treatment affects the household incomes, increased premature retirement and unemployment which, over time, could have a significant economical impact on the society \citep{Yach2006}.\\

\noindent
As more of the younger generation is gaining weight and becoming obese, having the risks and disease burden associated with obesity at such early age are not ideal -- both economically and epidemiologically -- and poses a threat to the growing population that are becoming more obese.
